Constant-round Blind Classical Verification of Quantum Sampling

### 2020-08-16 qpip0.tex
Make QPIP0 intro easier to understand

In this section, we combine the core protocol from \cite{FOCS:Mahadev18a}, which we restate as Protocol~\ref{proto:urmila4} \Ethan{Just say $\PiMeasure$}, with \Cref{QPIP1thm} to create a delegation protocol for $\SampBQP$ for fully classical clients. A direct composition results in Protocol~\ref{proto:qpip0_naive}. However, as we will see in \Cref{sec:urmila4}, Protocol~\ref{proto:urmila4} has a peculiar and weak guarantee, so \Cref{proto:qpip0_naive} don't have any reasonable completeness and soundness. To boost its soundness, we run $m=\poly(\lambda)$ copies in parallel and test on $m-1$ copies of them, resulting in Protocol~\ref{proto:QPIP0samp}. We use techniques from \cite{arXiv:ChiaChungYam19} to prove that Protocol~\ref{proto:QPIP0samp} has soundness error \Ethan{Phrase in terms of accuracy param instead} $1/\sqrt{m}$.

\Ethan{Go even more high level. This roadmap is confusing to people who aren't familiar with the relevant literature}

@@

In her groundbreaking work, Mahadev gives a $\QPIP_0$ protocol for $\BQP$ languages.
The core of this work is a 4-round $\QPIP_0$ protocol $\PiMeasure$ that allow a $\BQP$ prover to ``commit a state" for a classical verifier to choose a measurement basis and obtain corresponding measurement results.
One can see $\cVGS$ as a $\QPIP_1$ protocol where the prover sends copies of ground state to the verifier to measure;
which can then be transformed to a $\QPIP_0$ protocol by replacing the verifier's measurement with calls to $\PiMeasure$.

The details of $\PiMeasure$ is as follows. The verifier chooses a string $h$ specifying the measurements he wants to make, and generates keys $pk, sk$ from $h$. It sends $pk$ to the prover. The prover ``commits" to a state $\rho$ of its choice using $pk$ and replies with its commitment. \Ethan{Need more intuition} The verifier then uniformly chooses between two options: do a \emph{testing round} or do a \emph{Hadamard round}. He sends his choice to the prover, and prover replies accordingly. If the verifier chose testing round, he checks the prover's reply against the previous commitment, and rejects if he sees an inconsistency. If the verifier chose the Hadamard round, he calculates $M_{XZ}(\rho, h)$ based on the reply. \cite{FOCS:Mahadev18a} shows a ``binding" property of $\PiMeasure$: if a prover would always succeed on the testing round, then there exists some $\rho$ so that the verifier obtains $M_{XZ}(\rho, h)$ if he had chosen Hadamard round, no matter what $h$ the verifier has picked at the beginning.

@@

$\PiMeasure$ has negligible completeness errors.
On the other hand, as the verifier learns the measurement outcome only on Hadamard round, the protocol offers no standard soundness guarantees;
instead, it achieves the following \emph{binding property} that gives weaker guarantees against cheating provers.

>>>>

\Ethan{The following two paragraphs have been rewritten to be more high-level}

In this section, we create a delegation protocol for $\SampBQP$ with fully classical clients following the approach taken in \cite{FOCS:Mahadev18a}.
The core protocol, $\PiMeasure$, allows a $\BQP$ prover to ``commit a state" for a classical verifier to choose a measurement basis and obtain corresponding measurement results.
By asking the prover to prepare and commit copies of a certificate for the client to verify, one obtains a $\QPIP_0$ protocol for $\BQP$.

Composing our $\PiSamp$ with $\PiMeasure$ directly, however, results in $\PiNaive$ which does not provide reasonable completeness or accuracy guarantees.
This is due to $\PiMeasure$ itself having peculiar and weak guarantees:
particularly, the client doesn't always obtain measurement outcomes even if the server were honest.
To overcome this challenge, we run $m=\poly(\lambda)$-copies of $\PiNaive$ in parallel to produce a constant-round $\PiSampZ$.
Using techniques from \cite{arXiv:ChiaChungYam19}, we prove that $\PiSampZ$ has accuracy error $O(1/\sqrt{m})$.

@@

$\PiMeasure$ is a 4-round protocol played between a verifier (which corresponds to our client) and a prover (which corresponds to our server).
The first two rounds are similar to the typical commit phase.
The verifier chooses a string $h$ specifying the measurements he wants to make, and generates keys $pk, sk$ from $h$. It sends $pk$ to the prover. The prover ``commits" to a state $\rho$ of its choice using $pk$ and replies with its commitment $y$.
\Ethan{Fix the following...}
The verifier at this point chooses between the ability to catch cheating provers and generate outputs.
If it suspects a prover is cheating, it runs a \emph{testing round},
which catches cheating provers at the cost of obtaining outputs.
Otherwise it runs a \emph{Hadamard round},
where it obtains a potentially incorrect output depending on whether the prover cheats.

The verifier then uniformly chooses between two options: do a \emph{testing round} or do a \emph{Hadamard round}. He sends his choice to the prover, and prover replies accordingly. If the verifier chose testing round, he checks the prover's reply against the previous commitment, and rejects if he sees an inconsistency. If the verifier chose the Hadamard round, he calculates $M_{XZ}(\rho, h)$ based on the reply.

@@

$\PiMeasure$ has negligible completeness errors.
It also gives the following \emph{binding property} against cheating provers:
if a prover would always succeed on the testing round, then there exists some $\rho$ so that the verifier obtains $M_{XZ}(\rho, h)$ if he had chosen Hadamard round, no matter what $h$ was chosen at the beginning.
\Ethan{Say somewhere that a ``prover" is fully described by two unitaries}
